Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-16 authors.tex
Updated authors list

\textbf{Erwan Le Masson}$^{26}$,

@@

\textbf{Dan McGlinn}$^{27\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Christoph Metzner}$^{28\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Owen Petchey}$^{29\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Hans Ekkehard Plesser}$^{30\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Timothée Poisot}$^{31\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Karthik Ram}$^{32\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Yoav Ram}$^{33\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Etienne Roesch}$^{34\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Cyrille Rossant}$^{35\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Vahid Rostami}$^{36\S}$,

@@

\textbf{Aaron Shifman}$^{37\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Joseph Stachelek}$^{38\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Marcel Stimberg}$^{39\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Frank Stollmeier}$^{40\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Adam Tomkins}$^{41\ddagger}$,

@@

\textbf{Federico Vaggi}$^{42\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Guillaume Viejo}$^{43\S}$,

@@

\textbf{Julien Vitay}$^{44\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Anya Vostinar}$^{45\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
\textbf{Roman Yurchak}$^{46\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
\textbf{Tiziano Zito}$^{47\dagger}$\\

>>>>

\textbf{Dan McGlinn}$^{26\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Christoph Metzner}$^{27\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Owen Petchey}$^{28\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Hans Ekkehard Plesser}$^{29\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Timothée Poisot}$^{30\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Karthik Ram}$^{31\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Yoav Ram}$^{32\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Etienne Roesch}$^{33\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Cyrille Rossant}$^{34\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Vahid Rostami}$^{35\S}$,

@@

\textbf{Aaron Shifman}$^{36\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Joseph Stachelek}$^{37\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Marcel Stimberg}$^{38\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Frank Stollmeier}$^{39\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Federico Vaggi}$^{40\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Guillaume Viejo}$^{41\S}$,

@@

\textbf{Julien Vitay}$^{42\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Anya Vostinar}$^{43\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Roman Yurchak}$^{44\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Tiziano Zito}$^{45\dagger}$\\
